\section{Purpose}

\subsection{Purpose of the Platform}
SafeStreets is a service that aims to improve the safety of the general traffic.
This is achieved by creating a community of users who are able to report any violation they see while the system manages
all the aspects of data validation and statistical analysis.
Different services contribute to this purpose:
\begin{itemize}
  \item The first service offered by the front end application is the report service. Any registered user can submit violation reports and SafeStreets will validate them as described in the following sections with the help of the community.
  \item The second service offered by the front end application is the the Unsafe Areas Map. SafeStreets will provide statistics about areas that have a higher risk of violations based on the reports it receives and the danger of the infractions. Data can also be collected from public services if available to increase accuracy.
  \item The third service is the ticket generation. Traffic policemen will have access to a dedicated section of the application where SafeStreets will collect validated reports. This will enable any registered policeman to take actions against those violations.
\end{itemize}

\subsection{Purpose of this document}
In this document a more detailed approach with respect to the RASD will be provided to explain how we intend to build the platform. The following paragraphs
will describe the architecture of the physical system and its abstract software components, how they interact with each other and how they create the services
we described in the RASD.