\section{Purpose}

\subsection{General Purpose}
SafeStreets is a service that aim to improve the safety of the general traffic.
This is achieved by creating a community of users who are able to report any violation they see while the system manages
all the aspects of data validation and statistical analysis.
Different services contribute to this purpose:
\begin{itemize}
  \item The first service offered by the front end application is the report service. Any registered user can submit violation reports and SafeStreets will validate them as described in the following sections with the help of the community.
  \item The second service offered by the front end application is the the Unsafe Areas Map. SafeStreets will provide statistics about areas that have a higher risk of violations based on the reports it receives and the danger of the infractions. Data can also be collected from public services if available to increase accuracy.
  \item The third service is the ticket generation. Traffic policemen will have access to a dedicated section of the application where SafeStreets will collect validated reports. This will enable any registered policeman to take actions against those violations.
\end{itemize}

\subsection{Goals}
The following goals describe the key points of our system:
\begin{itemize}
  \item G1: the system will provide an easy interface for violation reports
  \item G2: the system will provide aggregate anonymous data to show unsafe areas
  \item G3: the system will show violation reports to registered authorities
  \item G4: the system will integrate a validation procedure that will be followed strictly for each submitted report
  \item G5: the system will provide secure authentication methods
  \item G6: user data will only be available to the user itself, authorities and SafeStreets authorized employees
\end{itemize}

\subsection{Scope}
SafeStreets is a service that will be offered to any citizen having a valid ID number.
The service will create a direct channel to communicate with authorities and to other users about the observed traffic violations, promoting street safeness and
helping others who might be in need, for example by reporting a vehicle which is blocking an access for disabled people.
Registered users will be able to submit reports that will be validated by other end-users, creating a network of trust.
Reports will be filled by users with information about the violation, the location and the license plate of the subject. This will make reports detailed enough for
approval by public officers that will be able to review them and take proper actions to discourage further infractions.